{How do we copy and paste?\\The semantic drift of quotations in blogspace}

### 2015-02-19 brains-conclusion.tex
ack / updated post-telmo

% !TEX root = brainscopycut.tex
\section{Concluding remarks}\label{sec:conclusion}
We aimed to contribute to the empirical understanding of knowledge transformation processes by studying a simple task where individuals are \emph{implicitly} trying to reproduce textual content. To some extent, our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
In more detail, we describe the joint properties of the substituted and substituting terms in the reformulation by individuals of a specific type of utterances (quotations). %--- in this sense we also diverge from psycholinguistic experiments that focus on ease of recall.

>>>>

% !TEX root = brainscopycut.tex
\section{Concluding remarks}\label{sec:conclusion}
We aimed to contribute to the empirical understanding of representation transformation processes %\marginnote{fixed after Telmo saying: Is this really about knowledge transformation of more about representation transformations and the insight they provide over underlaying cognitive processes?}
 by studying a simple task where individuals are \emph{implicitly} trying to reproduce textual content. To some extent, our work amounts to a large \emph{in vivo} experiment where we appraise the impact of classically-influent psycholinguistic variables in the accuracy of the reproduction.
In more detail, we describe the joint properties of the substituted and substituting terms in the reformulation by individuals of a specific type of utterances (quotations). %--- in this sense we also diverge from psycholinguistic experiments that focus on ease of recall.

### 2015-02-19 brains-protocol.tex
ack / updated post-telmo

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around a casual expression, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
We thus filter out all clusters lasting more than 80 days, and all quotes less than 5 words long %\seb{it is asymmetrical...}
 (as well as quotes not written in English).
We eventually keep 19,621 clusters (out of 71,568; i.e. 27.4\%), containing a total of 60,246 unique quotes (out of 310,457; i.e. 19.4\%) making up $\sim$838k occurrences (out of 8.12m, i.e. 10.3\%).
The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.\footnote{\TB{While we lose real event-related utterances such as ``the terrorists have used automatic weapons and in some places grenades have been lobbed the encounters are still going on and we are trying to overpower them''} \rk{T: it is not clear why this utterance is lost according to the filtering rules described in sections 3.1}, we contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion. We manually checked on a subsample of clusters that a large proportion of remaining quotes seem to be relevant, while filtered quotes are essentially irrelevant.}

@@

We can thus show how words are modified once we know they are substituted, \hbox{i.e.} how their features are modified by said substitution.
We therefore measure how \TB{a word $\wstart$'s feature} \rk{T: This is correct but confusing. I had to re-read 3 times.} varies as $\wstart$ is substituted for $\warrival$, i.e. $\phi(\warrival)$ as a function of $\phi(\wstart)$.
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$, i.e.:\footnote{To avoid possible autocorrelation effects due to substitutions belonging to the same cluster (which are likely not statistically independent and may lead to overly optimistic confidence intervals), we first average substitutions over each cluster, by considering the average of arrival word features for a given start word.}
$$\nu_{\phi}(f) = \left<\phi(\warrival)\right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$

>>>>

Manual inspection of this dataset revealed that it contains a significant number of everyday language quotations (such as ``it was much better than I expected'', ``did that just happen'', as well as many simple expletive-based sentences).
Their presence is largely due to random variations around a casual expression, while we are interested in transformations of news-related quotes causally linked to an original, identifiable utterance.
We thus filter out all clusters lasting more than 80 days, and all quotes less than 5 words long %\seb{it is asymmetrical...}
 (as well as quotes not written in English).
We eventually keep 19,621 clusters (out of 71,568; i.e. 27.4\%), containing a total of 60,246 unique quotes (out of 310,457; i.e. 19.4\%) making up $\sim$838k occurrences (out of 8.12m, i.e. 10.3\%).
The significantly larger loss in occurrences indicates that, on average, the clusters we lose contain more occurrences than those we keep, which is expected for everyday language utterances.\footnote{While we lose some real event-related utterances because of their presence in clusters lasting more than 80 days (such as ``the terrorists have used automatic weapons and in some places grenades have been lobbed the encounters are still going on and we are trying to overpower them''), we contend that the use of the unfiltered dataset would strongly jeopardize results related to linguistic evolution or information diffusion. We manually checked on a subsample of clusters that a large proportion of remaining quotes seem to be relevant, while filtered quotes are essentially irrelevant.}

@@

We can thus show how words are modified once we know they are substituted, \hbox{i.e.} how their features are modified by said substitution.
Considering a word $\wstart$ substituted for $\warrival$, we measure how the feature of $\wstart$ varies when it is replaced with $\warrival$, i.e. we look at $\phi(\warrival)$ as a function of $\phi(\wstart)$. 
Averaging this value over all start words such that $\phi(w) = f$ yields the mean variation for that feature value~$f$, i.e.:\footnote{To avoid possible autocorrelation effects due to substitutions belonging to the same cluster (which are likely not statistically independent and may lead to overly optimistic confidence intervals), we first average substitutions over each cluster, by considering the average of arrival word features for a given start word.}
$$\nu_{\phi}(f) = \left<\phi(\warrival)\right>_{\left\lbrace \wstart\rightarrow\warrival | \phi(\wstart) = f \right\rbrace}$$

### 2015-02-19 brainscopycut.tex
Garbage is garbage
ack / updated post-telmo

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Jean-Pierre Nadal, Sharon Peperkamp, and Nicolas Baumard for useful suggestions and comments.

@@

\clearpage 
\input{brains-garbage}

>>>>

We are warmly grateful to Ana Sofia Morais for her precious feedback and advice on this research, and to Telmo Menezes, Jean-Pierre Nadal, Sharon Peperkamp, and Nicolas Baumard for useful suggestions and comments.

@@

%\clearpage 
%\input{brains-garbage}
